Verification of concurrent design patterns with data

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
see def 10

The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties. The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism. 
Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms. This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification. \textbf{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}

@@

For a component $B$, we denote $S_{\semopen{B}}$ and
$s^0_{\semopen{B}}$ the corresponding constituents of
$\semopen{B}$.

>>>>

The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties. The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism. 
Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms. This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification. \noteLH{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}\noteEM{j'ai prefere abstraire...}

@@

For a component $B$, we denote $S_{\semopen{B}}$ and
$s^0_{\semopen{B}}$ the corresponding constituents of
$\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).
